Token-level author diarization using clustering of stylistic contexts

### 2017-05-30 paper/paper.tex
Small changes.

\citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks. First subtask is traditionally called intrinsic plagiarism detection (IPD). The goal of this task is to find plagiariarized parts of a document in which 70\% of text is written by main author and the rest by one or more other authors. The term \textit{intrinsic} means that a decision whether plagiarized parts exist or not has to be made only by analysing a given document, without any comparisons with external sources. In the rest of the paper we refer to this subtask as a task \textit{a}.

@@

\section{The proposed approaches}
clustering, sliding window
pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering

clustering metric

>>>>

\citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks. First subtask is traditionally called intrinsic plagiarism detection (IPD). The goal of this task is to find plagiariarized parts of a document in which 70\% of text is written by main author and the rest by one or more other authors. The term \textit{intrinsic} means that a decision whether plagiarized parts exist has to be made only by analysing a given document, without any comparisons with external sources. In the rest of the paper we refer to this subtask as a task \textit{a}.

@@

\section{Author diarization and intrinsic plagiarism detetion ()}
% describe the problem
% define formally: document, segmentation, segment, author assignement (label)
% define evaluation metrics

Let $\Delta$ be the domain of documents. We define a document $D\in \Delta$ as a finite sequence of tokens $(t_i)_{i=1}^n$, where $n$ can differ among documents. Given a document, each of its tokens is unique and defined by its character sequence and position in the document. Therefore, a document can be equivalently represented by its set of tokens $T_D=\{t_i\}_{i=1}^n$.

For each document, there is a corresponding mapping to a sequence of labels $(a_i)_{i=1}^n$ that are representing groupings of tokens by authors. The labels $a_i$ are indices of authors of the document. Each token $t_i\in T_D$ is assigned a document-level label $a_i \in \{1..m\}$ associating it to one of $m$ authors. The exact value of the label is not important. It is only required that all tokens corresponding to the same author have the same label. Therefore, there are $m!$ equivalent such mappings given a document.

In the case of intrinsic plagiarism detection, there are only $2$ labels: $0$ representing the main author, and $1$ representing plagiarized text.

Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$. A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ represents a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each is assigned the same label. For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
\begin{equation}
	\bigcup_{s\in S}s = T_D  \wedge \bigcap_{s\in S}s = \{\}.
\end{equation}
The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.

Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations., i.e. $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$. Our goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e. makes good predictions given unseen documents.

\subsection{Evaluation measures}

For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's perfromance. The main measures are binary macro-averaged nad micro-averaged precision ($P$), recall (R) and $F_1$-score. For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$ measures proposed by \citet{rosales-mendez-2013}, which are specialized for evaluation of clustering results.

Let $l$ be a function that associates lengths in characters to segments. Specially, $l(\{\}) = 0$. For notational convenience, we also use $l$ to denote the sum of lengths of all segments in a set of segments: $l(S) = \sum_{s\in S} l(s),$ where $S$ is as set of segments. Given a document $D$, let $S_\mathrm{p} \subseteq \sigma(D)$ be a set of all true plagiarism segments of the document and $\hat{S}_\mathrm{p} \subseteq \hat{\sigma}(D)$ the segments predicted as plagiarism by the  model. With ${S_\mathrm{tp} = \bigcup_{(s,\hat{s})\in S_\mathrm{p}\times\hat{S}_\mathrm{p}} l(s\cap\hat{s})}$, the micro-averaged evaluation measures for intrinsic plagiarism detection are defined as follows:
\begin{align}
P_\mu &= \frac{l(\hat{S}_\mathrm{tp})}{l(\hat{S}_\mathrm{p})}, \\
R_\mu &= \frac{l(\hat{S}_\mathrm{tp})}{l(S_\mathrm{p})}, \\
F_\mu &= \frac{2}{P_\mu^{-1}+R_\mu^{-1}}.
\end{align}
The macro-average evaluation measures treat all plagiarism segments as equally important and are not affected by their lengths:
\begin{align}
P_M &= \frac{1}{|\hat{S}_\mathrm{p}|}
	\sum_{\hat{s}\in\hat{S}_\mathrm{p}}
		\frac{{\sum_{s\in S_\mathrm{p}} l(s\cap\hat{s})}}{l(\hat{s})}, \\
R_M &= \frac{1}{|S_\mathrm{p}|}
	\sum_{\hat{s}\in S_\mathrm{p}}
		\frac{{\sum_{s\in \hat{S}_\mathrm{p}} l(s\cap\hat{s})}}{l(s)}, \\
F_M &= \frac{2}{P_M^{-1}+R_M^{-1}}.
\end{align}

\section{The proposed approach}
% clustering, sliding window
% pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
% define the pipeline formally P = (f_p: d\times->t, f_b: t->\phi, f_t: \phi->\phi', c: \phi'->labels, f_s: labels\times d->s)
% describe GroupRepel loss, describe AutoKMeans, 
% clustering metric
